Getting start

### 2023-05-10 inst/gitbook/01_getting_started.Rmd
Update 01_getting_started.Rmd

<!-- ## An illustrative example -->
## A verbose example: mammals disparity through the K-Pg extinction {kpgexample}

Ar Macarface is studying the evolution of mammalian disparity (i.e. diversity of shapes) across the Cretaceous-Palaeogene mass extinction event (K-Pg - 66 million years ago).

Looking at this curve, Ar wants to know whether disparity increased as a response to the K-Pg mass extinction or not.
To do this, they need to check whether changes in disparity can actually be detected due to an extinction event (e.g. if an extinction event happens, does that change disparity curves?).
As a subsidiary question, they want to know whether the pattern is more likely due to a selective or random extinction event.

## Setting the stopping rule (stop after 30 time units)
stop_rule <- list(max.time = 30)

```{r}
## Converting the data to be passed to dispRity functions
dispRity_data <- dispRitreats(sim_data)

@@

>>>>

@@

## An illustrative example: mammals disparity through the K-Pg extinction {kpgexample}

Bib is studying the evolution of mammalian disparity (i.e. diversity of shapes) across the Cretaceous-Palaeogene mass extinction event (K-Pg - 66 million years ago).

Looking at this curve, Bib wants to know whether disparity increased as a response to the K-Pg mass extinction or not.
To do this, they need to check whether changes in disparity can actually be detected due to an extinction event (e.g. if an extinction event happens, does that change disparity curves?).
As a subsidiary question, they want to know whether the pattern is more likely due to a selective or random extinction event.

## Setting the stopping rule (stop after reaching 50 taxa)
stop_rule <- list(max.taxa = 50)

```{r, message = FALSE}
## Converting the data to be passed to dispRity functions
dispRity_data <- dispRitreats(sim_data)
